### 2020-02-26 ncov.tex
funding and stuff

>>>>

\section*{Funding}

BMB and DJDE were supported by Natural Sciences and Engineering Research Council (NSERC). ML was supported by Canadian Institutes of Health Research (CIHR). The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

\section*{Declaration of interests}

We declare no competing interests.

\section*{Acknowledgements}

We thank Daihai He for providing helpful comments on the manuscript.

\section*{Contribution}

SWP and JD developed the statistical framework. 
SWP reviewed the published literature.
SWP performed the analysis. 
SWP, BMB, and JD created the figures. 
SWP and JD wrote the first draft.
All authors contributed to the writing and approval of the final report.

\section*{Data availability}

\texttt{R} code is available in GitHub (\url{https://github.com/parksw3/nCoV_framework}).
